---
title: "Example Vignette"
vignette: >
  %\VignetteIndexEntry{example}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

```{r setup, include=FALSE}
brand <- yaml::read_yaml(brand::brand_file())
palette <- brand$color$palette

swatch <- function(value) {
  hex <- if (value %in% names(palette)) palette[[value]] else value
  paste0(
    '<span style="display:inline-block;width:12px;height:12px;',
    "background-color:",
    hex,
    ";margin-right:5px;",
    'border:1px solid #ccc;vertical-align:middle;"></span>`',
    hex,
    "`"
  )
}

for_mode <- function(value, mode) {
  if (is.list(value)) value[[mode]] else value
}
```

## Typography

## H2

Header 2

### H3

Header 3

#### H4

Header 4

Paragraph text should use the brand base font. Inline code should use the brand monospace: `const x = 42`.

```text
text block should use the brand monospace.
abcdefghijklmnopqrstuvwxyz 0123456789
```

```{r}
brand::use_brand
```

## Theme colors (semantic)

Read straight out of `_brand.yml`, the same file that styles this site.

```{r}
#| echo: false
tokens <- setdiff(names(brand$color), "palette")
knitr::kable(
  data.frame(
    Token = tokens,
    Light = vapply(tokens, function(t) swatch(for_mode(brand$color[[t]], "light")), ""),
    Dark = vapply(tokens, function(t) swatch(for_mode(brand$color[[t]], "dark")), "")
  ),
  row.names = FALSE,
  escape = FALSE
)
```

## Palette (named swatches)

These are the single-value entries under `color.palette`.

```{r}
#| echo: false
knitr::kable(
  data.frame(
    Name = names(palette),
    Value = vapply(names(palette), swatch, "")
  ),
  row.names = FALSE,
  escape = FALSE
)
```

## Components

::: {.callout-note}
Info callout.
:::

::: {.callout-warning}
Warning callout.
:::

::: {.callout-important}
Danger callout.
:::

::: {.callout-tip}
Tip callout.
:::

::: {.callout-caution}
Caution callout.
:::

> Blockquote example. This should remain readable in both light and dark modes.

### Table

| Item | Example |
|---|---|
| Link | <https://www.visruth.com> |
| Inline code | `printf("hello")` |
| List | - one<br>- two<br>- three |
