---
title: "Example Vignette"
vignette: >
  %\VignetteIndexEntry{example}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

```{r setup, include=FALSE}
yml <- yaml::read_yaml(system.file("pkgdown/_brand.yml", package = "brand", mustWork = TRUE))
pal <- yml$color$palette

c_val <- function(name, mode) {
  val <- yml$color[[name]][[mode]]
  hex <- if (val %in% names(pal)) pal[[val]] else val
  paste0('<span style="display:inline-block;width:12px;height:12px;background-color:', hex, ';margin-right:5px;border:1px solid #ccc;vertical-align:middle;"></span>`', hex, '`')
}

p_val <- function(name) {
  hex <- pal[[name]]
  paste0('<span style="display:inline-block;width:12px;height:12px;background-color:', hex, ';margin-right:5px;border:1px solid #ccc;vertical-align:middle;"></span>`', hex, '`')
}
```

## Typography

## H2

Header 2

### H3

Header 3

#### H4

Header 4

Paragraph text should use the brand base font. Inline code should use the brand monospace: `const x = 42`.

```text
text block should use the brand monospace.
abcdefghijklmnopqrstuvwxyz 0123456789
```

```{r}
brand::use_brand
```

## Theme colors (semantic)

The values below are pulled from `_brand.yml` using the `brand` shortcode.

| Token | Light | Dark |
|---|---|---|
| background | `r c_val("background", "light")` | `r c_val("background", "dark")` |
| foreground | `r c_val("foreground", "light")` | `r c_val("foreground", "dark")` |
| primary | `r c_val("primary", "light")` | `r c_val("primary", "dark")` |
| secondary | `r c_val("secondary", "light")` | `r c_val("secondary", "dark")` |
| success | `r c_val("success", "light")` | `r c_val("success", "dark")` |
| info | `r c_val("info", "light")` | `r c_val("info", "dark")` |
| warning | `r c_val("warning", "light")` | `r c_val("warning", "dark")` |
| danger | `r c_val("danger", "light")` | `r c_val("danger", "dark")` |

## Palette (named swatches)

These are the single-value entries under `color.palette`.

| Name | Value |
|---|---|
| ivory | `r p_val("ivory")` |
| ink | `r p_val("ink")` |
| blackish | `r p_val("blackish")` |
| cobalt | `r p_val("cobalt")` |
| periwinkle | `r p_val("periwinkle")` |
| slate | `r p_val("slate")` |
| mist | `r p_val("mist")` |
| haze | `r p_val("haze")` |
| shadow | `r p_val("shadow")` |
| teal | `r p_val("teal")` |
| amber | `r p_val("amber")` |
| rose | `r p_val("rose")` |

## Components

::: {.callout-note}
Info callout.
:::

::: {.callout-warning}
Warning callout.
:::

::: {.callout-important}
Danger callout. 
:::

::: {.callout-tip}
Tip callout.
:::

::: {.callout-caution}
Caution callout.
:::

> Blockquote example. This should remain readable in both light and dark modes.

### Table

| Item | Example |
|---|---|
| Link | <https://www.visruth.com> |
| Inline code | `printf("hello")` |
| List | - one<br>- two<br>- three |
